On the combination of Set Functions and Failures

### 2012-09-21 docs/src/manual.tex

\item[\fbox{\code{+/-interactive}}]\pindex{interactive}
Turn on/off the interactive mode.
In the interactive mode, the next non-deterministic value
is only computed when the user requests it.
In this mode, the computation is performed in a separate
window created by the command \code{interactivecommand}
whose value is defined in \ccode{.kics2rc}
(see Section~\ref{sec-customization}).

>>>>

\item[\fbox{\code{+/-interactive}}]\pindex{interactive}
Turn on/off the interactive mode.
In the interactive mode, the next non-deterministic value
is only computed when the user requests it.
Thus, one has also the possibility to terminate the
enumeration of all values after having seen some values.
